---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ronda

<!-- badges: start -->
<!-- badges: end -->

The primary goal of `ronda` is to simplify the conversion of R packages
into a format that can be easily installed and managed via Conda, enhancing
interoperability between R and other programming environments supported
by Conda.

## Installation

You can install the development version of ronda from its
[source repository](https://github.com/sales-lab/ronda) with:

``` r
# install.packages("pak")
pak::pak("sales-lab/ronda")
```

You will also need to install Miniconda. We recommend
using the conda-forge installer, available at
<https://conda-forge.org/download/>.

After installing Miniconda, create and activate a new environment with the
necessary build tools.

```bash
conda create -n ronda conda-build rattler-build rattler-index
conda activate ronda
```


## Usage

Here's a simple example of how to use `ronda` to build Conda packages for
some popular R packages.

```{r example}
library(ronda)
ronda_build(c("cli", "jsonlite"))
```

Once the procedure is completed successfully, the packages will be available
in the `conda-bld` subdirectory of your main Conda environment. You can use
`conda env list` to locate this directory.
